Physics 785 Term Paper: Turbulence in Molecular Clouds: Origins \& Impacts

### 2013-02-25 phys785/paper/paper.tex
Finished the writing (first draft)

\section{Basic Turbulence Theory}
\subsection{Kolmogorov's 1941 Theory}
Nearly all modern theories of turbulence are build upon the Kolmogorov's 1941
theory \citep{kolm1991}.  The Kolmogorov theory of turbulence describes locally
homogeneous, locally isotropic turbulence (a reasonable assumption for turbulent
flow with large Reynolds numbers, which certainly holds in all the phases of the
ISM).  Kolmogorov proposed two key hypotheses. The first is that the distribution 
of velocities in a turbulent flow are uniquely determined by the viscosity 
$\nu$ and the average specific dispersion energy rate $\epsilon$,  From 
this, a characteristic length $\eta$ and velocity $\sigma$:
$$\eta = \nu^{3/4}\epsilon^{1/4}$$
$$\sigma = \sqrt{\nu/\epsilon}$$
The second hypothesis is that on scales much larger than $\eta$, the turbulent flow
is uniquely determined \textit{only} by $\epsilon$.  These two assumptions
allow you to uniquely determine a energy spectrum as a function of wavenumber
$k$:
$$E(k) \propto \epsilon^{2/3}k^{-5/3}$$
The Kolmogorov energy spectrum has been the foundation of nearly all susbsequent
theories of turbulence.  The negative power law slope can be seen as the cascade
of energy down from large scale turbulent motions down to scales where viscous
dissipation becomes important ($\lambda \approx \eta$).
\subsection{MHD Turbulence}
Modern theories of turbulence in molecular clouds rely on the interplay between
"pure" fluid turbulence, and turbulence within magnetic fields.  By storing
energy within these fields, the decay of turbulence can be delayed long enough
to allow more modest energy sources to drive the turbulence observed in
molecular clouds.  \citet{shu1987} reports magnetic field strengths in a number
of molecular clouds on the order of $10-100 \mu G$.  Simple virial/equipartition
arguments suggest that thermal, turbulent, and magnetic energies within a cloud
should be roughly equal.

@@

MHD also provides new modes for turbulent energy to decay.  Ohmic heating and
ambipolar diffusion can convert turbulent energy within the fluid directly into
heat, and dynamo processes can pull kinetic energy out of the fluid and store it
in magnetic fields.  3D simulations of MHD turbulence suggest it decays in
approximately $\tau_{cross} = L/v_{rms}$, where $L$ is the scale of the cloud,
and $v_{rms}$ is the rms turbulent velocity. In environments like molecular
clouds, where turbulence is highly supersonic, the effects of MHD vs. "pure"
hydrodynamic turbulence may be small \citep{elm2004}

@@

Once a molecular cloud has begun forming stars, stellar feedback can provide
ample energy to drive both bulk and turbulent motions within clouds.
\citet{agertz2012} reports that stars typically return 
$\approx 10^{34} erg s^{1-} M_\odot^{-1}$ in the form of stellar winds and
supernovae.  Massive stars also produce ionizing UV, generating HII regions that
can shock the surrounding molecular gas.  With even conservative estimates of
efficiencies between the feedback rates, stellar feedback combined with
turbulence generated by fluid instabilities in the formation of molecular clouds
provides sufficient energy to power the observed turbulence within molecular
clouds\citep{elm2004}.  The chaotic driving of supernovae blasts and wind-carved
bubbles on a scale of $50-500pc$ (ie, on the scales comparable tot the total
cloud size), which then cascades down the to smaller scales.
\section{Impact of Turbulence on Cloud Structure \& Evolution}
\subsection{Cloud Formation}
\subsection{Turbulent Pressure Support}
Observations of molecular clouds provide two perplexing facts, namely that they
are typically cold (10-100K), and massive (much larger than the Jeans mass
$M_J$) \citep{gold1978}.  Yet they do not show evidence of rapid collapse, or of being the
extremely short lived objects that these facts would imply.  This suggests that
a there is some sort of non-thermal pressure supporting these clouds.
In molecular clouds that are in hydrostatic equilibrium, determining the sources
of pressure that supports the clouds against gravitational collapse is key in
determining which clouds will collapse, and why.  Non-thermal pressure support is
essential to allow super-Jeans mass clouds to persist.

Treating the energy within a volume's turbulence as  asource of pressure was
proposed as early as \citet{chandra1951}, where the Jeans stability criteria is
modified from:
$$\lambda_J = 2\pi \sqrt{\frac{c_s^2}{4\pi G\rho}}$$
where $c_s$ is the soundspeed, to a smaller value derived using the mean
turbulent velocity $u$:
$$\lambda_J = 2\pi \sqrt{\frac{c_s^2+u^2/3}{4\pi G\rho}}$$
For molecular clouds, where turbulence tends to be highly supersonic, this can
act to significantly increase the stability of a cloud against gravitational
collapse.
\subsection{Mixing \& Chemistry}
\subsection{Larson's Laws \& Star formation}
Strangely, turbulence can both support clouds (on a global scale), and cause
collapse (on smaller scales) \citep{mac2004}.  Since molecular cloud
turubulence is often supersonic, it is well beyond the incompressible regime,
and can produce density perturbations that can then collapse to form
stars\citep{elm2004}. Turbulence in nascent starforming 
regions is a critical element in the modern theory 
of starformation. One of the earliest works proposing this connection is
\citet{larson1981}.  Building on previous "merging bubble/shell" models of
molecular clouds and the larger ISM from works such as \citet{norman1980} and
\citet{mckee1977}, Larson used $^{13}CO$ observations of Taurus, $\rho$
Ophiucus, Orion, and a number of other clouds to determine a the mass function
of clouds within these clumps.  By measuring the velocity dispersions of these
clouds, along with their dimension, he observed that $\sigma \propto L^{0.38}$
(the ``size-linewidth" relation).  Since this value is close to the Kolmogorov
real-space power law slope $1/3$, \citet{larson1981} argued that the size of
clumps within molecular clouds was determined primarily by turbulence within
the cloud.

One of the most interesting recent developments is the suggestion by
\citet{hopk2013} that the
shape and universality of the stellar initial mass function is the result of 
turbulent dynamics within
starforming clouds. \citet{hopk2013} proposes a model of gravo-turbulent
fragmentation using the excursion set formalism similar to that previously used 
succesfully to predict the Halo Mass Function and clustering rates in
large-scale cosmological structures by \citet{press1974}.  By applying this tool
to the turbulent fluid of a molecular cloud, and tracking the first and last
crossings of overdense perturbations (see figure NUM), the mass function of
protostellar cores, (and thus the IMF) can be predicted using Monte Carlo
realizations of the turbulent density spectrum.  This analytic framework
can be used to generally predict the mass function from fragmentation
on any scale from essentially first principles (including the formation 
of clouds themselves, if they do in fact
form from turbulent fragmentation).  This framework suggests that gravitational
collapse of turbulent overdensity is the dominant driving force for much of the
substructure within molecular clouds.
\section{Conclusion}

\begin{thebibliography}{}
	\bibitem[Chandrasekhar(1951)]{chandra1951} Chandrasekhar, S.\ 1951, 
		Royal Society of London Proceedings Series A, 210, 26 
	\bibitem[Iroshnikov(1964)]{irosh1964} Iroshnikov, P.~S.\ 1964, 
		\sovast, 7, 566 
	\bibitem[Press \& Schechter(1974)]{press1974} Press, W.~H., \& Schechter, P.\
			1974, \apj, 187, 425 
	\bibitem[McKee \& Ostriker(1977)]{mckee1977} McKee, C.~F., \& Ostriker,
			J.~P.\ 1977, \apj, 218, 148 
	\bibitem[Goldsmith \& Langer(1978)]{gold1978} Goldsmith, P.~F., \& Langer,
			W.~D.\ 1978, \apj, 222, 881 
		\bibitem[Larson(1979)]{larson1979} Larson, R.~B.\ 1979, \mnras, 
		186, 479 
	\bibitem[Norman \& Silk(1980)]{norman1980} Norman, C., \& Silk, J.\ 
		1980, \apj,	238, 158 
	\bibitem[Larson(1981)]{larson1981} Larson, R.~B.\ 1981, \mnras, 
		194, 809 
	\bibitem[Shu, Adams \& Lizano(1987)]{shu1987} Shu, F. H., Adams, F.C.,
		Lizano, S.\ 1987 \araa, 25, 23
	\bibitem[Balbus \& Hawley(1991)]{balb1991} Balbus, S.~A., \& Hawley, J.~F.\
			1991, \apj, 376, 214 
	\bibitem[Kolmogorov(1991)]{kolm1991} Kolmogorov, A.~N.\ 1991, 
		Royal Society of London Proceedings Series A, 434, 9 
	\bibitem[Evans (1999)]{evans1999} Evans, N. J.\
			1999, \araa, 37, 311
	\bibitem[Mac Low(1999)]{mac1999} Mac Low, M.-M.\ 1999, \apj, 
		524, 169 
	\bibitem[Brunt(2003)]{brunt2003} Brunt, C.~M.\ 2003, \apj, 583, 
		280 
	\bibitem[Elmegreen \& Scalo(2004)]{elm2004} Elmegreen, B.~G., \& Scalo, J.\
			2004, \araa, 42, 211 
	\bibitem[Scalo 	\& Elmegreen(2004)]{scalo2004} Scalo, J., \& Elmegreen, B.~G.\
			2004, \araa, 42, 275
	\bibitem[Mac Low \& Klessen(2004)]{mac2004} Mac Low, M.-M., \& Klessen,
		R.~S.\ 2004, Reviews of Modern Physics, 76, 125 
	\bibitem[Tielens(2010)]{tiel2010} Tielens, A.~G.~G.~M.\ 2010, 
		The Physics and Chemistry of the Interstellar Medium, by 
		A.~G.~G.~M.~Tielens, Cambridge, UK: Cambridge University Press,	2010
	\bibitem[Crutcher(2012)]{crutch2012} Crutcher, R.~M.\ 2012, \araa,
		50, 29 
	\bibitem[Agertz et al.(2012)]{agertz2012} Agertz, O., Kravtsov, 
		A.~V., Leitner, S.~N., \& Gnedin, N.~Y.\ 2012, arXiv:1210.4957 
	\bibitem[Hopkins(2013)]{hopk2013} Hopkins, P.~F.\ 2013,
		\mnras, 729 
	\bibitem[Scannapieco(2013)]{scan2013} Scannapieco, E.\ 2013, \apjl, 763, L31 
\end{thebibliography}
\end{document}

>>>>

\section{Basic Turbulence Theory}
\subsection{Kolmogorov's 1941 Theory}
Nearly all modern theories of turbulence are build upon the Kolmogorov's 1941
theory \citep{kolm1991}.  The Kolmogorov theory of turbulence describes locally
homogeneous, locally isotropic turbulence (a reasonable assumption for turbulent
flow with large Reynolds numbers, which certainly holds in all the phases of the
ISM).  Kolmogorov proposed two key hypotheses. The first is that the distribution 
of velocities in a turbulent flow are uniquely determined by the viscosity 
$\nu$ and the average specific dispersion energy rate $\epsilon$,  From 
this, a characteristic length $\eta$ and velocity $\sigma$:
$$\eta = \nu^{3/4}\epsilon^{1/4}$$
$$\sigma = \sqrt{\nu/\epsilon}$$
The second hypothesis is that on scales much larger than $\eta$, the turbulent flow
is uniquely determined \textit{only} by $\epsilon$.  These two assumptions
allow you to uniquely determine a energy spectrum as a function of wavenumber
$k$:
$$E(k) \propto \epsilon^{2/3}k^{-5/3}$$
The Kolmogorov energy spectrum has been the foundation of nearly all susbsequent
theories of turbulence.  The negative power law slope can be seen as the cascade
of energy down from large scale turbulent motions down to scales where viscous
dissipation becomes important ($\lambda \approx \eta$).
\subsection{MHD Turbulence}
Modern theories of turbulence in molecular clouds rely on the interplay between
``pure" fluid turbulence, and turbulence within magnetic fields.  By storing
energy within these fields, the decay of turbulence can be delayed long enough
to allow more modest energy sources to drive the turbulence observed in
molecular clouds.  \citet{shu1987} reports magnetic field strengths in a number
of molecular clouds on the order of $10-100 \mu G$.  Simple virial/equipartition
arguments suggest that thermal, turbulent, and magnetic energies within a cloud
should be roughly equal.

@@

MHD also provides new modes for turbulent energy to decay.  Ohmic heating and
ambipolar diffusion can convert turbulent energy within the fluid directly into
heat, and dynamo processes can pull kinetic energy out of the fluid and store it
in magnetic fields.  3D simulations of MHD turbulence suggest it decays in
approximately $\tau_{cross} = L/v_{rms}$, where $L$ is the scale of the cloud,
and $v_{rms}$ is the rms turbulent velocity. In environments like molecular
clouds, where turbulence is highly supersonic, the effects of MHD vs. ``pure"
hydrodynamic turbulence may be small \citep{elm2004}

@@

Once a molecular cloud has begun forming stars, stellar feedback can provide
ample energy to drive both bulk and turbulent motions within clouds.
\citet{agertz2012} reports that stars typically return 
$\approx 10^{34} erg s^{1-} M_\odot^{-1}$ in the form of stellar winds and
supernovae.  Massive stars also produce ionizing UV, generating HII regions that
can shock the surrounding molecular gas.  With even conservative estimates of
efficiencies between the feedback rates, stellar feedback combined with
turbulence generated by fluid instabilities in the formation of molecular clouds
provides sufficient energy to power the observed turbulence within molecular
clouds\citep{elm2004}.  The chaotic driving of supernovae blasts and wind-carved
bubbles on a scale of $50-500pc$ (ie, on the scales comparable tot the total
cloud size), which then cascades down the to smaller scales.
\section{Impact of Turbulence on Cloud Structure \& Evolution}
\subsection{Cloud Formation}
The largest effect of turbulence on molecular clouds may not be intra-cloud
phenomena, but instead the actual \textit{formation} of clouds.
\citet{larson1981} suggested from his observations that cloud lifetimes were on
the order of $10^7 yr$, about twice their free-fall time.  If most clouds are
this young, this implies that clouds are both formed and destroyed on a
relatively continuous and rapid basis. Recent simulation results from
\citet{hopk2011} support this picture of a constantly replenished supply of
short-lived GMCs, and some suggest that even shorter lifetimes of a few $10^6$
years are more likely \cite{mac2004}.

Early models of cloud formation relied on a hierarchical merger type picture of
cloud collision and coalescence to explain the production of giant molecular
clouds from the atomic and ionized medium.  \citet{larson1981} reports that
these models fail to produce the production rates needed to sustain the observed
abundance of molecular clouds in the galaxy in light of their relatively short
lifetime (these models were developed with the assumption that cloud lifetimes
were on the order of $10^8 yr$).  Turbulence within the larger ISM can produce, 
in the highly compressible supersonic regime obeserved, strong density perturbations and
clumpy, filiamentary structures like that seen in figure NUM.  \citet{val2004}
presents a picture of supersonic turbulence or colliding flows producing thin, 
shocked sheets that then fragments to form molecular clouds. Coupled with
thermal multiphase instabilities, this can act to rapidly build dense clumps
that will quickly become molecular clouds as atomic hydrogen becomes molecular
on dust grains and the high densities of the cloud allow for self-shielding.
The dominant theory of cloud formation currently is that shocks, from turbulence
and supernovae, build large overdensities where molecule formation is very
rapid, and that cloud dispersal by feedback (or the same turbulent flow that
can form them) happens on the order of a roughly 1-10 Myr.
\subsection{Turbulent Pressure Support}
Observations of molecular clouds provide two perplexing facts, namely that they
are typically cold (10-100K), and massive (much larger than the Jeans mass
$M_J$) \citep{gold1978}.  This, coupled with their relatively short lifetimes,
seems to imply that they collapse gravitationally relatively quickly after they 
form.  However, measurements of star formation efficiency within these clouds,
and of the relative stellar mass fractions of the milky way and other galaxies
tells us that these clouds only convert a small fraction of their mass into
stars \citep{mac2004}, and that their lifetimes are in fact longer than their
free-fall times. This suggests that
a there is some sort of non-thermal pressure supporting these clouds, in
addition to processes that can disrupt or destroy clouds before they can convert
most of their mass into stars. While disruption of clouds by feedback can reduce
their star formation efficiency (by destroying them after they form only a few
massive stars)\citep{hopk2011}, the observation of super-Jeans mass clouds that
are older than the time needed for them to collapse needs this additional
mechanism to keep clouds supported.
In molecular clouds that are in hydrostatic equilibrium, determining the sources
of pressure that supports the clouds against gravitational collapse is key in
determining which clouds will collapse, and why.  Non-thermal pressure support is
essential to allow super-Jeans mass clouds to persist.

Treating the energy within a volume's turbulence as  asource of pressure was
proposed as early as \citet{chandra1951}, where the Jeans stability criteria is
modified from:
$$\lambda_J = 2\pi \sqrt{\frac{c_s^2}{4\pi G\rho}}$$
where $c_s$ is the soundspeed, to a smaller value derived using the mean
turbulent velocity $u$:
$$\lambda_J = 2\pi \sqrt{\frac{c_s^2+u^2/3}{4\pi G\rho}}$$
For molecular clouds, where turbulence tends to be highly supersonic, this can
act to significantly increase the stability of a cloud against gravitational
collapse.
\subsection{Mixing \& Chemistry}
Molecular clouds, being \textit{molecular}, are sites in which more 
complicated ISM chemistry can occur.  Since these clouds are extremely dense and
cool, while many of the reactants for forming simple ($CO$, $HCN$, etc.) and
complex (PAHs, amino acids, etc) are abundant, the conditions in the molecular
cloud are often not ideal for slow, steady formation of these compoounds.
PDRs at the edge of clouds can catalyze the formation of some compounds, but
destroy others.  Many of the compounds in molecular clouds have negative heats
of formation, implying they would form extremely slowly at the mean $\approx
10K$ temperatures in the cloud.  In addition to this, chemical reaction networks
found that early-time solutions to time-dependent evolution equations (rather
than equalibrium concentrations) matched most closely the observed abundances in
molecular clouds\citep{scalo2004}.

Turbulence offers an explanation for all of these observations.  Since the
interiors of clouds are not isotropic in density, temperature, or UV flux,
turbulent mixing can transport species into regions where their production is
enhanced, and then spread the products into the rest of the cloud.  Decay of
turbulence and shock heatingcan result in local temperature increases, allowing 
endothermic reactions to produce species that otherwise would not be 
seen\citep{xie1995}.  MHD turbulence
can have a significant impact on ion-neutral reactions by magnetically forcing
ions, producing an effectively faster mixing rate for ionized species.
\subsection{Larson's Laws \& Star formation}
Strangely, turbulence can both support clouds (on a global scale), and cause
collapse (on smaller scales) \citep{mac2004}.  Since molecular cloud
turubulence is often supersonic, it is well beyond the incompressible regime,
and can produce density perturbations that can then collapse to form
stars\citep{elm2004}. Turbulence in nascent starforming 
regions is a critical element in the modern theory 
of starformation. One of the earliest works proposing this connection is
\citet{larson1981}.  Building on previous "merging bubble/shell" models of
molecular clouds and the larger ISM from works such as \citet{norman1980} and
\citet{mckee1977}, Larson used $^{13}CO$ observations of Taurus, $\rho$
Ophiucus, Orion, and a number of other clouds to determine a the mass function
of clouds within these clumps.  By measuring the velocity dispersions of these
clouds, along with their dimension, he observed that $\sigma \propto L^{0.38}$
(the ``size-linewidth" relation).  Since this value is close to the Kolmogorov
real-space power law slope $1/3$, \citet{larson1981} argued that the size of
clumps within molecular clouds was determined primarily by turbulence within
the cloud.

One of the most interesting recent developments is the suggestion by
\citet{hopk2013} that the
shape and universality of the stellar initial mass function is the result of 
turbulent dynamics within
starforming clouds. \citet{hopk2013} proposes a model of gravo-turbulent
fragmentation using the excursion set formalism similar to that previously used 
succesfully to predict the Halo Mass Function and clustering rates in
large-scale cosmological structures by \citet{press1974}.  By applying this tool
to the turbulent fluid of a molecular cloud, and tracking the first and last
crossings of overdense perturbations (see figures NUM and NUM), the mass function of
protostellar cores, (and thus the IMF) can be predicted using Monte Carlo
realizations of the turbulent density spectrum.  This analytic framework
can be used to generally predict the mass function from fragmentation
on any scale from essentially first principles (including the formation 
of clouds themselves, if they do in fact
form from turbulent fragmentation).  This framework suggests that gravitational
collapse of turbulent overdensity is the dominant driving force for much of the
substructure within molecular clouds.

\section{Conclusion}
It is clear that on every scale related to the physics of molecular clouds, from
the atomic and molecular chemical processes within them, to the actual formation
of the clouds themselves, turbulence is a key ingredient.  Theoretical
predictions from as early as 1951, and observations from the 1970s confirmed
that turbulence was deeply related to the internal structure and evolution of
molecular clouds.  Recent work has continued to build upon this, suggesting that
the chemistry of the molecular ISM, and the mass function of stars are also 
closely tied to the turbulent motions within molecular clouds.  As simulations
and observations further constrain the energy spectrum, growth rate, and
dissipation of turbulence, a key component to building a unified picture 
of molecular cloud creation and destruction, star formation, and interstellar 
chemistry will be complete.
\begin{thebibliography}{}
	\bibitem[Chandrasekhar(1951)]{chandra1951} Chandrasekhar, S.\ 1951, 
		Royal Society of London Proceedings Series A, 210, 26 
	\bibitem[Iroshnikov(1964)]{irosh1964} Iroshnikov, P.~S.\ 1964, 
		\sovast, 7, 566 
	\bibitem[Press \& Schechter(1974)]{press1974} Press, W.~H., \& Schechter, P.\
			1974, \apj, 187, 425 
	\bibitem[McKee \& Ostriker(1977)]{mckee1977} McKee, C.~F., \& Ostriker,
			J.~P.\ 1977, \apj, 218, 148 
	\bibitem[Goldsmith \& Langer(1978)]{gold1978} Goldsmith, P.~F., \& Langer,
			W.~D.\ 1978, \apj, 222, 881 
	\bibitem[Larson(1979)]{larson1979} Larson, R.~B.\ 1979, \mnras, 
		186, 479 
	\bibitem[Norman \& Silk(1980)]{norman1980} Norman, C., \& Silk, J.\ 
		1980, \apj,	238, 158 
	\bibitem[Larson(1981)]{larson1981} Larson, R.~B.\ 1981, \mnras, 
		194, 809 
	\bibitem[Shu, Adams \& Lizano(1987)]{shu1987} Shu, F. H., Adams, F.C.,
		Lizano, S.\ 1987 \araa, 25, 23
	\bibitem[Balbus \& Hawley(1991)]{balb1991} Balbus, S.~A., \& Hawley, J.~F.\
			1991, \apj, 376, 214 
	\bibitem[Kolmogorov(1991)]{kolm1991} Kolmogorov, A.~N.\ 1991, 
		Royal Society of London Proceedings Series A, 434, 9 
	\bibitem[Xie et al.(1995)]{xie1995} Xie, T., Allen, M., 
		\& Langer, W.~D.\ 1995, \apj, 440, 674 
	\bibitem[Evans (1999)]{evans1999} Evans, N. J.\
			1999, \araa, 37, 311
	\bibitem[Mac Low(1999)]{mac1999} Mac Low, M.-M.\ 1999, \apj, 
		524, 169 
	\bibitem[Brunt(2003)]{brunt2003} Brunt, C.~M.\ 2003, \apj, 583, 
		280 
	\bibitem[Elmegreen \& Scalo(2004)]{elm2004} Elmegreen, B.~G., \& Scalo, J.\
			2004, \araa, 42, 211 
	\bibitem[Scalo 	\& Elmegreen(2004)]{scalo2004} Scalo, J., \& Elmegreen, B.~G.\
			2004, \araa, 42, 275
	\bibitem[Mac Low \& Klessen(2004)]{mac2004} Mac Low, M.-M., \& Klessen,
		R.~S.\ 2004, Reviews of Modern Physics, 76, 125 
	\bibitem[V{\'a}zquez-Semadeni et al.(2006)]{val2006}
		V{\'a}zquez-Semadeni, E., Ryu, D., Passot, T., Gonz{\'a}lez, R.~F., 
		\& Gazol, A.\ 2006, \apj, 643, 245 
	\bibitem[Tielens(2010)]{tiel2010} Tielens, A.~G.~G.~M.\ 2010, 
		The Physics and Chemistry of the Interstellar Medium, by 
		A.~G.~G.~M.~Tielens, Cambridge, UK: Cambridge University Press,	2010
	\bibitem[Hopkins et al.(2011)]{hopk2011} Hopkins, P.~F., 
		Quataert, E., \& Murray, N.\ 2011, \mnras, 417, 950 
	\bibitem[Crutcher(2012)]{crutch2012} Crutcher, R.~M.\ 2012, \araa,
		50, 29 
	\bibitem[Agertz et al.(2012)]{agertz2012} Agertz, O., Kravtsov, 
		A.~V., Leitner, S.~N., \& Gnedin, N.~Y.\ 2012, arXiv:1210.4957 
	\bibitem[Hopkins(2013)]{hopk2013} Hopkins, P.~F.\ 2013,
		\mnras, 729 
	\bibitem[Scannapieco(2013)]{scan2013} Scannapieco, E.\ 2013, \apjl, 763, L31 
\end{thebibliography}
\end{document}
